CF Registry Analysis

### 2022-12-12 Christine Chan/CF Registry/cf_registry_analysis.Rmd
might not need the apply stuff

df$A_IsOnEnzymes = factor(df$A_IsOnEnzymes,levels = 0:1,labels = c("No","Yes"))
df$A_salt_supplement = factor(df$A_salt_supplement,levels = 0:1,labels = c("No","Yes"))
df$A_cf_vitamins = factor(df$A_cf_vitamins,levels = 0:1,labels = c("No","Yes"))
df$A_dornasealfa = factor(df$A_dornasealfa,levels = 0:1,labels = c("No","Yes"))
df$A_pulmonarycomplications4 = factor(df$A_pulmonarycomplications4,

@@

df$A_pulmonarycomplications5 = factor(df$A_pulmonarycomplications5,

@@

df$A_othercomplications9 = factor(df$A_othercomplications9,

@@

df$A_hepatobiliary1_3 = factor(df$A_hepatobiliary1_3,

@@

```{r warning=FALSE,results='asis'}
# Summarize by ID and period
t1_df <- df %>%
  group_by(eDWID, Period) %>%
  summarise(
    Age = max(Age_YrEnd), Race = last(na.omit(Race)),
    Hispanic = last(na.omit(Hispanicrace)), Gender = last(na.omit(Gender)),
    `Patient Education` = last(na.omit(patient_education)),
    `Father Education` = last(na.omit(father_education)),
    `Mother Education` = last(na.omit(mother_education)),
    `Spouse Education` = last(na.omit(spouse_education)),
    `Marital Status` = last(na.omit(marital_status)),
    Employment = last(na.omit(employment)),
    Pregnancy = max(pregnant, na.rm = T)
  )
# Replace infinite values with missing
t1_df <- data.frame(lapply(t1_df, function(c) {
  c[is.infinite(c)] <- NA
  return(c)
}))
# Print table 1
cols <- colnames(t1_df)[3:ncol(t1_df)]
t1 <- tableby(as.formula(paste0("Period~", paste0("`", cols, "`", collapse = "+"))),
  data = t1_df
)
summary(t1)
```

>>>>

df$A_IsOnEnzymes = factor(df$A_IsOnEnzymes,ordered = T,

@@

df$A_salt_supplement = factor(df$A_salt_supplement,ordered = T,

@@

df$A_cf_vitamins = factor(df$A_cf_vitamins,ordered = T,

@@

df$A_dornasealfa = factor(df$A_dornasealfa,ordered = T,
df$A_pulmonarycomplications4 = factor(df$A_pulmonarycomplications4,ordered = T,
df$A_pulmonarycomplications5 = factor(df$A_pulmonarycomplications5,ordered = T,
df$A_othercomplications9 = factor(df$A_othercomplications9,ordered = T,
df$A_hepatobiliary1_3 = factor(df$A_hepatobiliary1_3,ordered = T,

@@

```{r warning=FALSE,results='asis'}
# Summarize by ID and period
t1_df <- df %>%
  group_by(eDWID, Period) %>%
  summarise(
    Age = max(Age_YrEnd), Race = last(na.omit(Race)),
    Hispanic = last(na.omit(Hispanicrace)), Gender = last(na.omit(Gender)),
    `Patient Education` = last(na.omit(patient_education)),
    `Father Education` = last(na.omit(father_education)),
    `Mother Education` = last(na.omit(mother_education)),
    `Spouse Education` = last(na.omit(spouse_education)),
    `Marital Status` = last(na.omit(marital_status)),
    Employment = last(na.omit(employment)),
    Pregnancy = max(pregnant, na.rm = T),
    .groups = "keep"
  )
# Replace infinite values with missing
t1_df <- data.frame(lapply(t1_df, function(c) {
  c[is.infinite(c)] <- NA
  return(c)
}))
# Print table 1
cols <- colnames(t1_df)[3:ncol(t1_df)]
t1 <- tableby(as.formula(paste0("Period~", paste0("`", cols, "`", collapse = "+"))),
  data = t1_df
)
summary(t1)
```
